---
title: "coralie hamon"
format: html
editor: visual
---

```{r}
#| message: false
library(here)
library(ggplot2)
library(dplyr)
library(tidyr)

here::i_am("intro-low-level-R.Rproj")
```

```{r}
typeof(1.5) # double
typeof("test") # character
typeof(TRUE) # logical
typeof(1L) # integer
typeof(1) # double
typeof(typeof) # closure : it's a function essentially
typeof(list()) # list
```

Every numbers are considered as double unless you specify it's an integer.

### Classes

```{r}
data(iris)
typeof(iris) # list
class(iris) # data frame

class(1) # numeric
class(1L) # integer
```

## Vector

### Introduction

Many things in R are vectors (and most of the other things are lists). A vector is a collection of values of the same type (possibly a single value).

```{r}
w <- 15.25
length(w)  # all vectors have a length
w[1]
```

The c-function can be seen as a creation function or, more accurately, as a vector concatenation function.

```{r}
y <- c(1,-2,45,1.5,-1e-10)
y
typeof(y)
y[2]
length(y)
```

### Character vectors

This is not R strength...

```{r}
z <- "alice"
length(z)  # 1
```

Salvation comes from 'stringr' package.

```{r}
library(stringr)
```

```{r}
str_length(z)  # 5
```

```{r}
char <- "😂😂😇"
str_length(char)
```

```{r}
some_values <- c("😂😂😇", "test")
some_values
length(some_values) # length of the vector
str_length(some_values) # length of each element in the vector
```

```{r}
x <- rnorm(5)
```

```{r}
y <- x
y
```

x and y can be understood as a value semantic assignment: "x" and "y" are different vectors with the same initial content.

Therefore modifying 'x' has no effect on 'y' (lazy copy).

# Indexing

```{r}
x[1] <- 18
x
y
```

```{r}
x
x[c(2, 2, 1, 4, 3)]
```

```{r}
x[0]

typeof(numeric(0))
length(numeric(0))

typeof(NA)
length(NA)
```

```{r}
x
x[c(1, 4)] <- c(-34, 42)
x[c(2, 10)] <- c(123, 70)
x

y <- c("A", "B", "C")
y
y[c(TRUE, FALSE, TRUE)]
```
