---
title: "Introduction to low Level R"
author: "Hao Xu"
format: html
---

## Types and Classes
### Types
```{r}
typeof(1.5)
typeof("toto")
typeof('also')
typeof(TRUE)
typeof(1L)
typeof(1) 
typeof(typeof)
typeof(list())
```

### Classes 

```{r}
data(iris)
typeof(iris)
class(iris)
```
## Vectors
### Introduction
Many things in R are vectors (and most of the other things are lists).

A vector is a collection of values of the same type (possibly a single value).

```{r}
x <- 15.25
length(x) ## all vectors have length
x[1]
```
```{r}
length(length(x))
typeof(length(x))
```
The 'c' function can be seen as a creation function or, more accurately, as a vector concatenation function.

```{r}
y <- c(1, -2, 45, 1.5, -1e-10)
y
typeof(y)
y[2]
length(y)
```
```{r}
c(x,y)
```
### Character vectors

This is not R strength...
```{r}
z <- "Alice"
length(z)
```
Salvation comes from the 'sting' package.
```{r}
library(stringr)
```
```{r}
str_length(z)
```
```{r}
complicated <- "ðŸ˜‚ðŸ˜ŠðŸ˜’ðŸ˜"
complicated
length(complicated)
str_length(complicated)
```
```{r}
some_values <-c("ðŸ˜‚ðŸ˜ŠðŸ˜’ðŸ˜","Ræ˜¯ä¸€é—¨å¾ˆå¥½çš„ç¼–ç¨‹è¯­è¨€","alice")
some_values
length(some_values)
str_length(some_values)
str_to_upper(some_values)

```
### Indexing
```{r}
x <- c(6,5,1,2,3,4)
x[3]
```
```{r}
x[4] <- 15
x
```
Assignment can be understood has a value semantic assignment: 'x' and 'y' are diffenrent vectors with the same initial content.
```{r}
y <- x
y
```
Therefore, modifying 'x' has no effect on 'y'
```{r}
x[1] <- 18
x
y
```
Indexing is made with vectors of 
```{r}
x
x[c(2,2,1,4,3)]

```
```{r}
x[0] ## no possible meaning -> empty numeric vector
x[7] ## no value
x[10]
```
```{r}
typeof(numeric(0))
length(numeric(0))
```
```{r}
typeof(NA)
length(NA)
```
```{r}
typeof(NA_integer_)
NA_integer_
```
```{r}
x
x[c(4,1,0,15)]
```
```{r}
c(numeric(0),5, numeric(0))
```
```{r}
x
x[c(-1,-4)]
```

```{r}
y <- c("A","B","C")
y
y[c(TRUE,FALSE,TRUE)]
```
```{r}
x
x[c(1,4)] <-c(-34,42)
x
x[c(2,10)] <-c(123,78)
x
```
















