---
title: "Main doc"
format: html
---

## Types and Classes
### Types
```{r}
typeof(1.5)
typeof("toto")
typeof('also')
typeof(TRUE)
typeof(1L)
typeof(1) 
typeof(typeof)
typeof(list())
```

### Classes 

```{r}
data(iris)
typeof(iris)
class(iris)
```
## Vectors
### Introduction
Many things in R are vectors (and most of the other things are lists).

A vector is a collection of values of the same type (possibly a single value).

```{r}
x <- 15.25
length(x) ## all vectors have length
x[1]
```
```{r}
length(length(x))
typeof(length(x))
```
The 'c' function can be seen as a creation function or, more accurately, as a vector concatenation function.

```{r}
y <- c(1, -2, 45, 1.5, -1e-10)
y
typeof(y)
y[2]
length(y)
```
```{r}
c(x,y)
```
### Character vectors

This is not R strength...
```{r}
z <- "Alice"
length(z)
```
Salvation comes from the 'sting' package.
```{r}
library(stringr)
```
```{r}
str_length(z)
```
```{r}
complicated <- "ðŸ˜‚ðŸ˜ŠðŸ˜’ðŸ˜"
complicated
length(complicated)
str_length(complicated)
```
```{r}
some_values <-c("ðŸ˜‚ðŸ˜ŠðŸ˜’ðŸ˜","Ræ˜¯ä¸€é—¨å¾ˆå¥½çš„ç¼–ç¨‹è¯­è¨€","alice")
some_values
length(some_values)
str_length(some_values)
str_to_upper(some_values)

```

# Indexing

```{r}
x[1] <- 18
x
y
```

```{r}
x
x[c(2, 2, 1, 4, 3)]
```

```{r}
x[0]

typeof(numeric(0))
length(numeric(0))

typeof(NA)
length(NA)
```

```{r}
x
x[c(1, 4)] <- c(-34, 42)
x[c(2, 10)] <- c(123, 70)
x

y <- c("A", "B", "C")
y
y[c(TRUE, FALSE, TRUE)]
```

